\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 scam.tex
.

\begin{example}[Van der Pol Oscillator]

@@

We use the Van der Pol oscillator benchmark
from~\cite{zutshi2014multiple} to demonstrate our falsification
approach. We want to check the property $P_3$, indicated by
the red box, given the initial set indicated by the green box. The
abstraction is defined by $\epsilon=0.2$, which results in an
evenly gridded state-space, where each cell is of size $0.2 \times
0.2$ units. $ScatterAndSimulate$ is then used to construct the
abstraction, using $2$ samples per cell and the time step
$\Delta = 0.1s$. The result is plotted in ~\figref{vdp-abs}.

@@

\section{An Example: Van der Pol Oscillator}
\todo{takes four iterations}
\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Cells and
trajectory segments used by $1$-relational modeling.}{vdp-map}

>>>>

\begin{example}[Van der Pol Oscillator]~\label{ex:vdp}

@@

We use the Van der Pol oscillator benchmark
from~\cite{zutshi2014multiple} to demonstrate our falsification
approach. We want to falsify property $P_3$, $x_{unsafe}\in[-1,
-6.5]$ and $y_{unsafe}\in[-0.7, -5.6]$, given the initial set
indicated $x0\in[-0.4, -0.4],\; y_0\in[0.4, 0.4]$. The abstraction
is defined by $\epsilon=0.2$, which results in an evenly gridded
state-space, where each cell is of size $0.2 \times 0.2$ units.
$ScatterAndSimulate$ is then used to construct the abstraction,
using $2$ samples per cell and the time step $\Delta = 0.1s$. The
result is plotted in ~\figref{vdp-abs}.

@@

\begin{example}
\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Cells and
trajectory segments used by $1$-relational modeling.}{vdp-abs-paths}

Going back to the example~\exref{vdp}, $ScatterAndSimulate$ is able to
    find several abstract trajectories as shown
    in~\figref{vdp-abs-paths}. However, typically, the refinement by
    increasing the quantization precision requires $4$ refinement
    iterations and finally finds a concrete counter-example for
    $\epsilon=0.125$.
\end{example}
